Anonymous provision of local services via blockchain

### 2022-02-25 access.tex
unify PoD, PoP definitions

\subsection{Proofs to justice}\label{proof-of-justice}
In case of dispute the customer can proof to the justice (police, court,
etc.) evidences that convinces the justice about the honesty of customer
and misbehaviour of SP. The reason why the SP can not start a dispute is
that the customer is anonymous, and therefore there is no personal
information to start a dispute against. To mitigate this issue the SP is
always in advantaged position, so that he has no reason to start a
dispute. The idea described further in section ~\ref{future-work}.

% Unify with what is writen in fiarness analysis

Abstracting from the services the SP is providing, in case of dispute
the customer should be able to prove that: (i) he delivered to the SP a
complete (according to the SP requirements) package, and the SP
accepted it; (ii) he paid for the transaction.

The first proof called proof-of-delivery (PoD) is a confirmation issued
by the SP to the customer.

\[\mathrm{PoD} = (\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

\item
  \(\mathrm{T}_\mathrm{issue}\) - time at which the PoD is issued.
\item
  \(\mathrm{T}_\mathrm{pay}\) - deadline to pay for the transaction.
\item
  \(\mathrm{T}_\mathrm{provide}\) - deadline to provide the service
  results.
\item
  \(\mathrm{nonce}\) - randomly generated number uniquely identifying
  the transaction.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

The second proof depend on the cryptocurrency implementation and is
discussed further section~\ref{payment-for-services}.

In case the SP has fulfilled the transaction and provide the results,
but the customer unjustly start a dispute, the SP is secured by the
proof of provision (PoP) he has published on the message board (described in section ~\ref{message-board}.

\[\mathrm{PoP} = (\mathrm{cid}, \mathrm{nonce}, \mathrm{sig}_\mathrm{SP})\]

\item
  \(\mathrm{cid}\) - content identifier as specified in section ~\ref{storage-network}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

By publishing the PoP on the blockchain, the SP can not falsify the time
at which the results has been provided, because the block creation time
proves that. Blockchain acts as a global clock that securely timestamps
everything that gets into the block, so the PoP that was included in a
block will be associated with the time when the block has been forged.
Moreover, since the blockchain is public, everyone (including the
justice) can be convinced that the SP indeed provided the results at
that time.

The connection between PoP and the results is made by the content
identifier which uniquely points to the results such that the PoP can
not forge results after the publication.

The content identifier is usually some kind of hash write about ipfs

\subsection{Message Board}\label{message-board}
The proof of provision that we coined for the purpose of this protocol
is generaly called the proof of existence
\cite{proofofexistence, de2016stampery, Chainpoi39}.

The idea behind proof of existence is to certify that some information
has existed at a certain moment of time, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
nonrepudiation requirement).

We need this functionality for two reasons: 1. Communicate the existence
of the results to the customer to whom the SP have no other
communication medium as the customer stays anonymous. 2. Let the SP to
proof the publication of results within the agreed with customer
deadline. Without such a proof there would be no other means to settle
the conflict between the customer claiming the results have not been
published and the SP claiming the results have been published within the
deadline.

@@

Such functionallity is the easiest to achieve by the trusted third party
that authoritatively tells what happend and when.

Bitcoin introduced a way of decentralising not only the currency system,
but also other similary working centralised trusted third parties
including the message board.

We let keep the protocol general enough to let the implementator use any
existing technology to provide message board service, with the
assumption that it's decentralised and supports subscribing for the
upcoming proofs from particular address.

@@

Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}. For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonimity.

@@

There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literaly gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity, allows uses to hide their real identity behind the pseudonim. Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be infered merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

@@

\begin{figure}[h!]
\caption{}
\centering
\includegraphics[width=9cm]{anonymity-diagram.png}
\label{fig:anonymity-diagram}
\end{figure}

Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP. Alice controls two blockchain addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from anonymous one. The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice. The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.

@@

\item
  \(\mathrm{cid}\) - content identifier as specified in ~\ref{storage-network}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction
  previosuly generated in PoD.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing
  non-repudiation.
\end{itemize}

@@

The first approach is more feasible in the near future. It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs (POD, POP, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers. Keeping the case fully confidential. The experts would be incentivised to participate in the pool by the system of fees. Their honest behaviour would be incentivised by the stake they would have to lock, and punishment they would get by judging incorrectly, where the ``correctly'' is determined by the quorum of votes.

>>>>

\subsection{Proofs to justice}\label{proof-of-justice}

In case of dispute the customer can proof to justice (police, court, etc.) convincing evidences for the honesty of the customer and misbehaviour of the SP. 
Because the customer is anonymous the SP can not start a dispute---there is no mean to identify the customer.

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in advantage position, therefore he has no reason to start a dispute. The customer on the other hand can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

Abstracting from the services the SP is providing, in case of dispute each party should be able to prove its honest behaviour. We introduce three proofs that should be disclosed to justice in case of a dispute:

\begin{enumerate}
    \item Proof-of-delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of: current time; deadline to pay for the transaction; and deadline to provide the service; deadline to provide the service results; randomly generated number uniquely identifying the transaction; and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction, at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.

    \item Proof-of-provision ($\mathrm{PoP}$) is an proof that the SP published the results at a certain time. It defend the SP in case the customer unjustly start a dispute after the results has been published. It consist of: content identifier as specified in section ~\ref{storage-network}; the value uniquely identifying the transaction previosuly generated in $\mathrm{PoD}$; the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the results is made by the content identifier which uniquely points to the results such that the $\mathrm{PoP}$ can not forge results after the publication.
\end{enumerate}

\subsection{Message Board}\label{message-board}
The proof-of-provision that we coined for the purpose of this protocol
is generally called the proof-of-existence
\cite{proofofexistence, de2016stampery, Chainpoi39}.

The idea behind proof-of-existence is to certify that some information
has existed at a certain moment of time, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
non-repudiation requirement).

We need this functionality for two reasons: (1) Communicate the existence
of the results to the customer to whom the SP have no other
communication medium as the customer stays anonymous; (2) let the SP to proof the publication of results within the agreed with customer deadline.

By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time
at which the results has been provided, because the block creation time
proves that. Blockchain acts as a global clock that securely timestamps
everything that gets into the block, so the $\mathrm{PoP}$ that was included in a
block will be associated with the time when the block has been created. Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the results at that time.

Without such a proof there would be no other means to settle the conflict between the customer claiming the results have not been published and the SP claiming the results have been published within the deadline.

@@

% Such functionallity is the easiest to achieve by the trusted third party that authoritatively tells what happened and when.

% Bitcoin introduced a way of decentralising not only the currency system,
% but also other similary working centralised trusted third parties
% including the message board.

We let keep the protocol general enough to let the implementer use any
existing technology to provide message board service, with the
assumption that it's decentralised and supports subscribing for the
upcoming proofs from particular address.

@@

Privacy is a concept used in almost all kinds of social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambigous definitions~\cite{smith2011information}. For the purpose of our work we rely on more concrete definitions, i.e.~confidentality and anonymity.

@@

There are also techniques that can be deployed on non-anonymous blockchains, the so called mixers that literally gather together users into an \textit{anonymity set}, which then collude together in order to launder the transactions, in such a way that to a observer the likelihood of the sender of each transaction was equiprobable for any user from the anonymity set.

Some systems guarantee pseudonomity rather than anonymity. Pseudonomity, allows uses to hide their real identity behind the pseudonym. Despite the whole system is transparent and allows linking actions to one identity, the system is considered anonymous as long as the link between pseudonym and real identity is secret. This assumption is hard to satisfy in practice, as the KYC (Know You Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity on most of the cryptocurrencies exchanges. This makes the anonymity of the user dependent on the security of the IT system. Moreover, some correlations can be infered merely by the analysis of transactions \cite{androulaki2013evaluating, ober2013structure}.

@@

\begin{figure}[h!]
\caption{Let us assume the Alice to be the customer willing to keep her identity private (anonymous) and Bob be the public SP. Alice controls two addresses 1 and 2, the connection between her real identity and the first address was compromised, and therefore the identification is possible, the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from anonymous one. The first action is confidential; therefore even though the psudonym has been compromised the action can not be associated with the Alice. The second action is transparent, therefore the Alice's anonymity is maintained as long as the connection to the second pseudonym is concealed.}
\centering
\includegraphics[width=9cm]{anonymity-diagram.png}
\label{fig:anonymity-diagram}
\end{figure}

@@

\item
  \(\mathrm{cid}\) - content identifier as specified in ~\ref{storage-network}.
\item
  \(\mathrm{nonce}\) - the value uniquely identifying the transaction previously generated in $\mathrm{PoD}$.
\item
  \(\mathrm{sig}_\mathrm{SP}\) - the SP's signature guaranteeing authentication.
\end{itemize}

@@

The first approach is more feasible in the near future. It would require creating large pool of experts in a field, that in case of dispute, would receive all the proofs ($\mathrm{PoD}$, $\mathrm{PoP}$, as well as any other proofs significant to the case) that could be queried by the experts in zero-knowledge fashion, i.e., they could ask limited number of questions to the proofs and getting yes/no answers. Keeping the case fully confidential. The experts would be incentivised to participate in the pool by the system of fees. Their honest behaviour would be incentivised by the stake they would have to lock, and punishment they would get by judging incorrectly, where the ``correctly'' is determined by the quorum of votes.
